Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-20 minimax.tex
new m14n9 data (and correction on T shirt dataset name)

The oracle is built as follows. 
For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}:\textit{T-Shirt} (researchers voted on tee shirt designs; $m \!=\! 11, n \!=\! 30$),
\textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$)
and \emph{Skate} (judges vote on skaters at the Euros Pairs Short Program; $m \!=\! 14, n \!=\! 9$).
% tee shirt designs voted by 
%$n \!=\! 30$ 
%members of the Optimization Research Group at NICTA;
% \textit{AGH Course Selection}: $m \!=\! 9$ courses evaluated by $n = 146$ students 
%of the AGH University; 
%and \emph{Skate}: $m \!=\! 14$ skaters evaluated by $n \!=\! 9$ judges at the Euros Pairs Short Program.
%We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
For the synthetic datasets, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn i.i.d. uniformly.
%independently and all have the same probability of appearing. 
We believe IC to be a challenging situation and expect the number of questions to ask, in order to reach a certain level of regret, to decrease with less varied profiles.
%We adopt IC because it is a more challenging situation: as can be expected intuitively , the number of questions to be asked decrease with less varied profiles. 
To generate the weights of the scoring rule, we first draw $m \!-\! 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.

@@

			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/normalizedLin.dat};
			\addlegendentry{m=5, n=10}
%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/normalizedLin.dat};
%			\addlegendentry{m=5, n=15}
			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/normalizedLin.dat};
			\addlegendentry{m=5, n=20}
			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/normalizedLin.dat};
			\addlegendentry{m=10, n=20}
			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/normalizedLin.dat};
			\addlegendentry{m=10, n=30}
			\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirt]{data/normalizedLin.dat};
			\addlegendentry{tshirts m11n30}
			\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/normalizedLin.dat};
			\addlegendentry{courses m9n146}
			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
			\addlegendentry{m=14, n=9}
			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/normalizedLin.dat};
			\addlegendentry{skate m14n9}
			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/normalizedLin.dat};
			\addlegendentry{m=15, n=30}
		\end{axis}
	\end{tikzpicture}
\end{figure}

@@

In \cref{fig:linearity} we can also observe, as expected, that given a problem size the number of questions needed to reach a given MMR is lower when considering real datasets rather than a synthetic profile generated according to IC. \commentBN{Add the following:}
Indeed, in the Skate dataset the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3; in Courses  all agents rank the same alternative at the top position,
while in \textit{T-Shirt}  the alternatives are evenly distributed in the preference rankings.
%By looking at the data we observe that:
%\begin{itemize}
%	\item \textit{Skate} - the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3;
%	\item \textit{AGH} - all agents rank the same alternative at the top position, different group of agents share the same preference rankings;
%	\item \textit{T Shirt} - the alternatives are evenly distributed in the preference rankings.
%\end{itemize}
%The experiments suggest that high degree of similarity in the preference rankings helps reducing the regret faster.
% do less harm than halving the gain in regret, on average.

>>>>

The oracle is built as follows. 
For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}:\textit{T Shirt} (researchers voted on T-shirt designs; $m \!=\! 11, n \!=\! 30$),
\textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$)
and \emph{Skate} (judges vote on skaters at the Euros Pairs Short Program; $m \!=\! 14, n \!=\! 9$).
% tee shirt designs voted by 
%$n \!=\! 30$ 
%members of the Optimization Research Group at NICTA;
% \textit{AGH Course Selection}: $m \!=\! 9$ courses evaluated by $n = 146$ students 
%of the AGH University; 
%and \emph{Skate}: $m \!=\! 14$ skaters evaluated by $n \!=\! 9$ judges at the Euros Pairs Short Program.
%We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
For the synthetic datasets, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn i.i.d. uniformly.
%independently and all have the same probability of appearing. 
We believe IC to be a challenging situation and expect the number of questions to ask, in order to reach a certain level of regret, to decrease with less varied profiles.
%We adopt IC because it is a more challenging situation: as can be expected intuitively , the number of questions to be asked decrease with less varied profiles. 
To generate the weights of the scoring rule, we first draw $m \!-\! 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.

@@

			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/normalizedLin.dat};
			\addlegendentry{m=5, n=10}
%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/normalizedLin.dat};
%			\addlegendentry{m=5, n=15}
			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/normalizedLin.dat};
			\addlegendentry{m=5, n=20}
			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/normalizedLin.dat};
			\addlegendentry{m=10, n=20}
			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/normalizedLin.dat};
			\addlegendentry{m=10, n=30}
			\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirt]{data/normalizedLin.dat};
			\addlegendentry{tshirts m11n30}
			\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/normalizedLin.dat};
			\addlegendentry{courses m9n146}
			%\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/m14n9.dat};
			\addlegendentry{m=14, n=9}
			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/normalizedLin.dat};
			\addlegendentry{skate m14n9}
			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/normalizedLin.dat};
			\addlegendentry{m=15, n=30}
		\end{axis}
	\end{tikzpicture}
\end{figure}

@@

In \cref{fig:linearity} we can also observe, as expected, that given a problem size the number of questions needed to reach a given MMR is lower when considering real datasets rather than a synthetic profile generated according to IC. \commentBN{Add the following:}
Indeed, in the Skate dataset the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3; in Courses  all agents rank the same alternative at the top position,
while in \textit{T Shirt}  the alternatives are evenly distributed in the preference rankings.
%By looking at the data we observe that:
%\begin{itemize}
%	\item \textit{Skate} - the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3;
%	\item \textit{AGH} - all agents rank the same alternative at the top position, different group of agents share the same preference rankings;
%	\item \textit{T Shirt} - the alternatives are evenly distributed in the preference rankings.
%\end{itemize}
%The experiments suggest that high degree of similarity in the preference rankings helps reducing the regret faster.
% do less harm than halving the gain in regret, on average.
